---
title: "botscan"
author: "Kurt Wirth"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A package extending the capability of [botometer](https://github.com/IUNetSci/botometer-python) 
by measuring suspected bot activity in any given Twitter query. This README is 
derived from Matt Kearney's excellent [rtweet]((https://github.com/mkearney/rtweet)) 
documentation.

## Install

Install from GitHub with the following code:

```{r install, eval = FALSE}
if (!requireNamespace("devtools", quietly = TRUE)) {
  install.packages("devtools")
}
devtools::install_github("kurtawirth/botscan")
```

This package connects <code>botometer</code> to <code>rtweet</code>. As a 
result, each user must have previously acquired authentication from Twitter and 
instructions to do that [can be found here](http://rtweet.info/articles/auth.html).

Users will also need to install the latest version of Python, as botscan 
accesses Python-based <code>botometer</code>, as well as acquiring a [Mashape 
key](https://market.mashape.com/OSoMe/botometer). Doing so requires a Mashape
account. BotOMeter's default rate limit is 2,000 inquiries per day, so users
are strongly encouraged to sign up for a (free) BotOMeter Pro key. Instructions 
to do that [can be found here](https://market.mashape.com/OSoMe/botometer-pro/pricing).

## Usage

There are two functions currently live for botscan. 

To begin, the user must first enter the following code, inserting their keys 
where appropriate:

```{setup instructions, eval = FALSE}
bom <- setup_botscan("YourMashapeKey", 
                     "YourTwitterConsumerKey", 
                     "YourTwitterConsumerSecret", 
                     "YourTwitterAccessToken", 
                     "YourTwitterAccessTokenSecret")
```

Currently, this must be done at the start of every session.

Next, the fun begins with <code>botscan</code>.

Its first argument takes any Twitter query, complete with boolean operators if
desired, surrounded by quotation marks.

The next argument determines how long an open stream of tweets will be
collected, with a default of 30 seconds. In order to gather a specific volume
of tweets, it is suggested that the user run a small initial test to determine
a rough rate of tweets for the given query. If the user prefers to use Twitter's
Search API, the next argument allows the user to specify the number of tweets
to extract.

The fourth argument determines whether retweets will be included if using the
Search API and the fifth takes a number, less than one, that represents the 
desired threshold at which an account should be considered a bot. The default 
is .430, a reliable threshold as described by BotOMeter's creator [here](http://www.pewresearch.org/fact-tank/2018/04/19/qa-how-pew-research-center-identified-bots-on-twitter/). 

The sixth argument allows the user to toggle between user-level and
conversation-level summaries.  The default is set to conversation-level
data, understood as the proportion of the queried conversation that is 
bot-related.  If <code>user_level</code> is set to <code>TRUE</code>, 
<code>botscan</code> will return user-level data, understood to be the 
proportion of the queried conversation's authors that are estimated to be bots.

The seventh argument allows the user to toggle between Twitter's Search and 
Streaming APIs. The default is set to using the Streaming API, as it is 
unfiltered by Twitter and thus produces more accurate data. Search API data is 
filtered to eliminate low quality content, thus negatively impacting 
identification of bot accounts.

The eighth argument allows the user to opt out of auto-parsing of data, 
primarily useful when dealing with large volumes of data. The ninth and final 
argument defaults to keeping the user informed about the progress of the tool 
in gathering and processing data with the <code>verbose</code> package but 
can be toggled off.

```{r usage, eval = FALSE}
## load botscan
library(botscan)

## Enter query surrounded by quotation marks
botscan("#rstats")
#> [1] 0.1642276

## Result is percentage - in this case, 16.42276%.

## If desired, choose the stream time and threshold
botscan("#rstats", timeout = 60, threshold = .995)
#> [1] 0.02398524

## Alternatively, choose to use Twitter's Search API and options associated with it.
botscan("#rstats", n_tweets = 1500, retweets = TRUE, search = TRUE, threshold = .995)
#> [1] 0.03270932

## Result is percentage - in this case, 2.398524%.

##If desired, scan only users rather than the conversation as a whole.
botscan("#rstats", user_level = TRUE)
#> [1] 0.1505155

## Result is percentage - in this case, 15.05155%.
```

This process takes some time, as botscan is currently built on a loop of 
BotOMeter. Efforts to mainstream this process are set as future goals. A 
standard pull of tweets via <code>botscan</code> processes approximately 11 to 
12 accounts per minute in addition to the initial tweet streaming.

Twitter rate limits cap the number of Search results returned to 18,000 every 
15 minutes. Thus, excessive use of <code>botscan</code> in a short amount of 
time may result in a warning and inability to pull results.  In this event, 
simply wait 15 minutes and try again.  In an effort to avoid the Twitter rate 
limit cap, <code>botscan</code> defaults to returning 1000 results when 
<code>search = TRUE</code>.
